Contracts for unions and intersections are hard for Nickel

### 2021-05-18 paper.tex
Add examples to Union/intersection section

>>>>

% Content:
%   - Unions are useful as a fundamental data block
%     Examples: nullable, tree-like data structure, multiple representations

\begin{lstlisting}
type BinaryTree =
Integer | (BinaryTree, BinaryTree)
\end{lstlisting}

\begin{lstlisting}
optionalValue : String | Null
\end{lstlisting}

\begin{lstlisting}
person : {name : String, age : Number}
  | {name : String, dateOfBirth : String}
\end{lstlisting}

%   - Intersections are useful for subtyping or refinement (integers/floats
%       e.g)
\begin{lstlisting}
1 : Int & Float
\end{lstlisting}
%   - Intersections are useful to encode overloading
\begin{lstlisting}
incr: (Int -> Int) & (Float -> Float)
\end{lstlisting}

%   - Intersections are useful to encode mixins (see Scala3)
\begin{lstlisting}
Comparator: {cmp: T -> T -> Bool}
Shower: {show: T -> String}

showSmaller : (dict: Comparator & Shower) -> T -> T -> String
\end{lstlisting}
%   - Intersections appears in some form as unions' dual
\begin{lstlisting}
\end{lstlisting}

% Things to settle: how to motivate them, how to compare them to ADTs. Purely
% dynamic approach, or typed approach too?
\newpage
